---
title: "Activity: Street or Road?"
author: "Jared Hayes"
output: html_notebook
---

## Load in the data

```{r}
#load libraries 
library(tidyverse)
#load in the data here 
# we will only be using the "street-addresses.csv" file from the text
download.file(url="https://mdbeckman.github.io/dcSupplement/data/CMS_ProvidersSimple.rds",
              destfile = "Data.rds")
DataTable <- readRDS("Data.rds")


```

## Recreate Solved Example using `sample(50)`

```{r}
Addresses <- read_csv("https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv")
Sample <- 
  Addresses %>%
  sample_n(size = 50)
pattern <- "BOX\\s+(\\d+)"

BoxNumbers <- 
  Sample %>%
  filter(grepl(pattern, address)) %>%
  tidyr::extract(address, into = "boxnum", regex = pattern)
```

## Recreate Soved Example using the entire `Address` data set

```{r}

all_box_numbers<-
  Addresses%>%
  filter(grepl(pattern, address)) %>%
  tidyr::extract(address, into = "boxnum", regex = pattern)

```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}
all_box_numbers%>%
  summarise(count=n())

```

My answer here...... 


## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl(" BOX ", address)
          )
```

My answer here.......
First line creates new variable 
Second line identifies data set we will be manipulating 
Third line finds strings that don't end with st, road or rd
Fourth line finds strings that aren't in the form of an apartment 
Fifth line finds strings that don't have the word box 

#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}

pattern <- "(ST|RD|ROAD|CIRCLE|DR|LN|CT|DRIVE|COURT|WAY|BLVD|PL|LOOP|PKWY|AVE|AVENUE|CV|CIR|LANE|TRAIL|TRL)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl("BOX ", address)
          )
endings<-
  Addresses%>%
  filter(grepl(pattern, address))%>%
  tidyr::extract(address, into = "streetEnding", regex = pattern)
```

My answer here.......

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}
ending_counts<-table(endings)
ending_counts_df<-data.frame(ending = names(ending_counts), count = as.vector(ending_counts))%>%
  arrange(desc(count))
ending_counts_df
```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}
ggplot(ending_counts_df, aes(x = reorder(ending, -count), y = count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Street Name Endings", x = "Ending", y = "Count") 
   
```

#### Additional Question 3: Comment on any patterns you see

My answer here.......

Road is most popular when adding together road and rd. 
Abbreviations are much more common than spelling out the whole word. 
There are a few endings with a load of addresses and a lot of endings with few addresses. 